### 2016-03-01 introduction.tex
fixes

Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  The solution Chen et al. proposed to this problem was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

Fuzzer taming results using FPF were promising, but limited.  Rather than proposing a universal metric for use in fuzzer taming, Chen et al. offered many possible metrics (based on ideas in the literature, such as edit distances \cite{lev} or coverage spectra \cite{RepsSpectra} methods), none of which performed notably well across all three benchmark data sets, and some of which were not even applicable to all of the data sets.  For the two most difficult benchmarks, none of the metrics performed extremely well. FPF-based approaches remain in need of a universal but effective metric, particularly for the critical first 50 test cases examined \cite{PLDI13}.

>>>>

In a PLDI 2013 paper, Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

Fuzzer taming results using FPF were promising, but limited.  Rather than proposing a universal metric for use in fuzzer taming, Chen et al. offered many possible metrics (based on ideas in the literature, such as edit distances \cite{lev} or coverage spectra \cite{RepsSpectra} methods), none of which performed notably well across all three benchmark data sets, and some of which were not even applicable to all data sets.  For the two most difficult benchmarks, none of the metrics performed extremely well. FPF-based approaches remain in need of a universal but effective metric, particularly for the critical first 50 test cases examined \cite{PLDI13}.

### 2016-03-01 relatedwork.tex
small fix related
fixes

The most closely related work is that of Chen et. al \cite{PLDI13}.  The present paper uses two of the same data sets, applies the FPF \cite{Gonzalez} algorithm, and has the same empirical focus of determining how to identify faults for complex compilers.  The primary difference is that the distance metrics used with FPF in the previous work were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper expands on Chen et al. by putting the FPF approach in the context of a much richer causal comparison of program executions that applies in theory to any executions, not just failing test cases.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  The work of Chen et. al \cite{PLDI13} provides an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.

>>>>

The most closely related work is that of Chen et. al \cite{PLDI13} (which shares one author with the present paper).  We use two of the same data sets, apply the FPF \cite{Gonzalez} algorithm, and have the same empirical focus of determining how to identify faults for complex compilers.  The primary difference is that the distance metrics used with FPF in the previous work were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper expands on Chen et al. by putting the FPF approach in the context of a much richer causal comparison of program executions that applies in theory to any executions, not just failing test cases.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  The work of Chen et. al \cite{PLDI13} provides an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.
